SMT-Boosted Security Types for Low-Level MPC

### 2025-11-07 toplas26/sty.tex
checkpoint

\begin{definition} Define $\ov(\Gamma)$ as follows:
\begin{eqnarray*}
\ov(\varnothing) &=& \varnothing \\[-1.5mm]
\ov(\setit{[\mx{z}{\cid}, \rx{y}{\cid'}] : \sharety} \cup \Gamma) &=& \setit{\mx{z}{\cid}} \cup \ov(\Gamma)\\[-1.5mm]
\ov(\setit{[\px{x} + \px{y}] : \pubty} \cup \Gamma) &=& \setit{\px{x},\px{y}} \cup \ov(\Gamma)\\[-1.5mm]
\ov(\setit{[\out{\cid}] : \outty} \cup \Gamma) &=& \setit{\out{\cid}} \cup \ov(\Gamma)
\end{eqnarray*}
\end{definition}

\begin{lemma}
  \label{lemma-sty-noninteractive-sound}
  Assume given $\eqspre \wedge \toeq{\prog}, \Gamma,R: {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\Gamma, \eqspre \wedge \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then, letting $X \defeq \ov(\Gamma) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$ for
  $\cid_1 \ne \cid_2$:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X \cup \setit{\phi_1 + \phi_2}}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup X \cup \setit{\phi_1 + \phi_2, \phi_1}}
  $$
\end{lemma}

>>>>

Next, we make a simple definition to formalize what we mean by the interactive
variables in the share type environment $\Gamma$.
\begin{definition} Define $\ov(\Gamma)$ as follows:
\begin{eqnarray*}
\ov(\varnothing) &=& \varnothing \\[-1.5mm]
\ov(\setit{[\mx{z}{\cid}, \rx{y}{\cid'}] : \sharety} \cup \Gamma) &=& \setit{\mx{z}{\cid}} \cup \ov(\Gamma)\\[-1.5mm]
\ov(\setit{[\px{x} + \px{y}] : \pubty} \cup \Gamma) &=& \setit{\px{x},\px{y}} \cup \ov(\Gamma)\\[-1.5mm]
\ov(\setit{[\out{\cid}] : \outty} \cup \Gamma) &=& \setit{\out{\cid}} \cup \ov(\Gamma)
\end{eqnarray*}
\end{definition}
Given the above, we can formulate our key Lemma about noninteractive typing
judgements, which tells us that individual shares in isolation don't reveal anything
about their reconstruction. This result follows by Theorem \ref{theorem-toeq}
and known homomorphic properties of secret sharing schemes. 
\begin{lemma}
  \label{lemma-sty-noninteractive-sound}
  Assume given $\eqspre \wedge \toeq{\prog}, \Gamma,R: {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\Gamma, \eqspre \wedge \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then, letting $X \defeq \ov(\Gamma) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$ for
  $\cid_1 \ne \cid_2$:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X \cup \setit{\phi_1 + \phi_2}}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup X \cup \setit{\phi_1 + \phi_2, \phi_1}}
  $$
\end{lemma}
